---
title: "BehavioralResults"
author: "Rebecca Martin"
date: "6/23/2018"
output: 
    github_document:
        df_print: 'kable'
        toc: true
        dev: png
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---

## Settings

```{r settings}
#knitr::opts_chunk$set(cache=TRUE)
```


```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
figureDir <- file.path(root, 'figures')
```

## Packages

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(bmlm)
library(arm)
```

## Read in data

```{r readData}
appAvgLong <- read.table(file.path(dataDir,"app_avg_long.txt"), header=TRUE, sep="\t") ## for graphing 
appAvgWide <- read.table(file.path(dataDir,"app_avg_wide.txt"), header=TRUE, sep="\t")
demographicsLong <- read.table(file.path(dataDir,"demographicsLong.txt"), header=TRUE, sep="\t")
appBehavLongRaw <- read.table(file.path(dataDir,"app_behav_long.txt"), header=TRUE, sep="\t")

# For BMI measurements
asegLong <- read.table(file.path(dataDir,"asegLong.txt"), header=TRUE, sep="\t")
```

## Calculate average reactivity score to use as a control for analyses

```{r reactivityScore}
appBehavLongRaw <- appBehavLongRaw %>% 
    dplyr::filter(Type == 'Close') %>% 
    group_by(ID, Phase, Type) %>% 
    summarize(AvgClose=mean(Rating, na.rm=TRUE)) %>% 
    ungroup() %>% 
    dplyr::select(-Type) %>% 
    right_join(appBehavLongRaw, by=c('ID'='ID', 'Phase'='Phase'))
```

## Clean and center data

```{r}
## Merge dataframes by id and phase
appLongAll <- merge(appBehavLongRaw, demographicsLong, by=c('ID', 'Phase'))
aseg2TPbehav <- merge(appAvgLong, asegLong, by=c('ID', 'Phase'))

## Bad subs: 10744, 13078, 1136
appAvgLong <- appAvgLong %>% dplyr::filter(ID != 10744, ID!= 13078, ID != 1136)
appAvgWide <- appAvgWide %>% dplyr::filter(ID != 10744, ID!= 13078, ID != 1136)
appLongAll <- appLongAll %>% dplyr::filter(ID != 10744, ID!= 13078, ID != 1136)

appAvgLongReduced <- appAvgLong %>% dplyr::select(Reactivity=Close, Regulation=Far, Age, fsid) %>% gather(key=Type, value=Rating, -fsid, -Age)

## Center data
appLongAll$AgeCent <- appLongAll$Age - mean(appLongAll$Age)
appLongAll$AgeSq <- appLongAll$AgeCent*appLongAll$AgeCent
appLongAll$AgeCu <- appLongAll$AgeCent*appLongAll$AgeCent*appLongAll$AgeCent

# Make Close and Far subsets for averaged and long data frames
appLongAvgClose <- appAvgLongReduced %>% filter(Type=="Reactivity")
appLongAvgFar <- appAvgLongReduced %>% filter(Type=="Regulation")

appLongClose <- appLongAll %>% filter(Type=="Close")
appLongFar <- appLongAll %>% filter(Type=="Far")
```

## Prep Graphs

```{r, make_theme, echo=FALSE, results='hide', message=FALSE}

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'), #color="black"
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        panel.grid.major=element_line(color="transparent"),
                        axis.title.x = element_text(size=24,face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16, face="bold"),
                        strip.text.x = element_text(size = 16, face="bold"),
                        legend.title = element_text(face="bold"),
                        axis.line.x=element_line(color = 'black'), 
                        axis.line.y=element_line(color = 'black'))
```

# Graphing

## Make longitudinal graph

```{r}
demographicsPlotter <- appAvgLong %>% 
    mutate(Age=as.numeric(as.character(Age))) %>% 
    group_by(fsid) %>% 
    mutate(AgeMin=min(Age), AgeMax=max(Age)) %>% 
    ungroup() %>% 
    arrange(AgeMin) %>% 
    mutate(subjid=factor(fsid, levels=unique(fsid)))

ggplot(demographicsPlotter) + geom_errorbarh(aes(xmin=AgeMin, y=subjid, xmax=AgeMax, x=Age, group=fsid), height=0) + geom_point(aes(x=Age, y=subjid, group=fsid)) + ylab(NULL) + beckys.theme.conference + theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) + xlim(5,26)

#ggsave("figures/demographics.pdf", width=7, height=5, dpi=300)
```

## Run regressions for behav figure

```{r}
## Effect of Age and Close/Far
### Close Regression
closeBehavRes <- lmer(Rating ~ AgeCent + (1 | fsid), data=appLongClose)
summary(closeBehavRes)

## Far Regression
farBehavRes <- lmer(Rating ~ AgeCent + (1 | fsid), data=appLongFar)  
summary(farBehavRes)

### Combined Regression
bothBehavRes <- lmer(Rating ~ AgeCent + Type + (Type | fsid), data=appLongAll) 
summary(bothBehavRes)

### Interaction of Strategy and Age
bothBehavResInt <- lmer(Rating ~ Type*AgeCent + (Type | fsid), data=appLongAll)
summary(bothBehavResInt)

### BMI Group
summary(BMIClose <- lmer(Close ~ BMIGroupReduced + (1 | ID), data=aseg2TPbehav))
summary(BMIFar <- lmer(Far ~ BMIGroupReduced + (1 | ID), data=aseg2TPbehav))

### BMI Percentile
## Filter so age under 21 since BMI perc measurements are not accurate after that age
aseg2TPbehavUnder21 <- aseg2TPbehav %>% dplyr::filter(Age < 21)
summary(BMIClosePerc <- lmer(Close ~ BMIPerc + (1 | ID), data=aseg2TPbehavUnder21))
summary(BMIFarPerc <- lmer(Far ~ BMIPerc + (1 | ID), data=aseg2TPbehavUnder21))
```

## Get fixed effect lines and confidence bands for Close and Far

```{r}
## for 95% confidence intervals change probs to 2.5 and 97.5 #90% = .05, .95
fitted.mer <- function(mod, nsim=100, probs=c(.025, .975), re.form=NULL)
{
    if(length(probs) != 2)
    {
        stop('probs must have two numbers, a lower and an upper bound')
    }
    
    predictThis <- function(x)
    {
        predict(x, re.form=re.form)
    }
    
    # compute bootstrapped predictions
    thePreds <- bootMer(mod, FUN=predictThis, nsim=nsim, re.form=re.form)
    
    # get the quantiles for each prediction and transpose to nice, row format
    theBounds <- apply(thePreds$t, 2, quantile, probs=probs) %>% t
    
    # combine the predictions and the quantils for each prediction and give names and make a tibble
    cbind(thePreds$t0, theBounds) %>% 
        as.data.frame %>% 
        setNames(c('Prediction', 'Lower', 'Upper')) %>% 
        tibble::as_tibble()
}

closeBehavResAvg <- lmer(Rating ~ Age + (1|fsid), data=appLongAvgClose)
farBehavResAvg <- lmer(Rating ~ Age + (1|fsid), data=appLongAvgFar)

closePreds <- fitted.mer(closeBehavResAvg, nsim=400, re.form=NA)
farPreds <- fitted.mer(farBehavResAvg, nsim=400, re.form=NA)

appLongClosePred <- bind_cols(appLongAvgClose, closePreds) %>% tibble::as_tibble()
appLongFarPred <- bind_cols(appLongAvgFar, farPreds) %>% tibble::as_tibble()

appLongAllPred <- bind_rows("Reactivity"=appLongClosePred, 
                            "Regulation"=appLongFarPred, 
                            .id='TrialType')

```

## Graph behav ME figure (longitudinal lines with smoothed fixed effects lines for close and far)

```{r}
ggplot(appLongAllPred, aes(x=Age)) + 
    #geom_smooth(aes(color=Type, fill=Type), level=.95, method='lm') +
    geom_point(aes(y=Rating, color=Type), size=1, alpha=.5) +
    geom_line(aes(y=Rating, group=fsid, color=Type), alpha=.5, size=.75) + 
    geom_ribbon(aes(ymin=Lower, ymax=Upper, fill=Type), alpha=.4) + 
    geom_line(aes(y=Prediction, color=Type), size=1) + 
    facet_wrap(~Type) + 
    beckys.theme.conference +
    ylab("Rating of Craving") + 
    ylim(1,5) +
    xlim(5,26) +
    scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") +
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", legend.title=element_blank())

#ggsave("figures/BehavMainEffects.pdf", width=10, height=5, dpi=300)
#ggsave("figures/BehavMainEffectsDiss.pdf", width=10, height=5, dpi=300)
```

# Run regressions 

## What is the shape of the behavioral changes? 

```{r}
### Close Regression
closeNull <-  lmer(Rating ~ 1 + (1 | fsid), data=appLongClose)
closeBehav <- lmer(Rating ~ AgeCent + (1 | fsid), data=appLongClose)
closeBehavSq <- lmer(Rating ~ AgeCent + AgeSq + (1 | fsid), data=appLongClose)
closeBehavCu <- lmer(Rating ~ AgeCent + AgeSq + AgeCu + (1 | fsid), data=appLongClose)

anova(closeNull, closeBehav, closeBehavSq, closeBehavCu)

## Far Regression
farNull <- lmer(Rating ~ 1 + (1 | fsid), data=appLongFar) 
farBehav <- lmer(Rating ~ AgeCent + (1 | fsid), data=appLongFar)  
farBehavSq <- lmer(Rating ~ AgeCent + AgeSq + (1 | fsid), data=appLongFar) 
farBehavCu <- lmer(Rating ~ AgeCent + AgeSq + AgeCu + (1 | fsid), data=appLongFar) 

anova(farNull, farBehav, farBehavSq, farBehavCu)
```

# Look at Annualized Change

## Make Data Long

```{r prepper}
appToPlot <- appAvgWide %>% 
    # only keep columns we care about
    dplyr::select(ID, Age_T1, CloseAnn, FarAnn) %>% 
    # make the data long, creating a column for both long and far, keeping Age and TimeElapsed separate
    gather(Type, DiffAnnual, CloseAnn, FarAnn) %>% 
    # group by subjid and Type so we can get proper lagged values 
    mutate(Type=ifelse(Type == 'CloseAnn', 'Reactivity', 'Regulation'))
```

## Plot Annualized Change

```{r plotter}
ggplot(appToPlot, aes(x=Age_T1, y=DiffAnnual)) + 
    geom_hline(yintercept=0, linetype="dashed", color="darkgrey") +
    geom_smooth(aes(color=Type, fill=Type), level=.9,  method="lm", fullrange=TRUE) + 
    geom_point(aes(color=Type), alpha=.3) + 
    facet_wrap(~Type) + 
    xlab("Age at Time 1") +
    ylab('Annualized Rating Change') +
    xlim(5,26) +
    theme(legend.position='none') + 
    beckys.theme.conference + 
    scale_color_brewer(palette="Set1") +
    scale_fill_brewer(palette="Set1") 

#ggsave("figures/AnnualizedChange.pdf", width=10, height=6, dpi=300)
```

## Does annualized change differ with age? 

```{r}
closeAnnMod <- lm(CloseAnn ~ Age_T1, data=appAvgWide)
summary(closeAnnMod)

farAnnMod <- lm(FarAnn ~ Age_T1, data=appAvgWide)
summary(farAnnMod)

# Control for reactivity at time 1
farAnnModCont <- lm(FarAnn ~ Age_T1 + p1Close, data=appAvgWide)
summary(farAnnModCont)

## Nope!!

## Cool interaction with parent income and close though
closeAnnParentInc <- lm(CloseAnn ~ Age_T1*ParentIncome_T1, data=appAvgWide)
summary(closeAnnParentInc)
```


## What is the best shape of rate of change? 
```{r}
closeAnnModSq <- lm(CloseAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appAvgWide)
closeAnnModCu <- lm(CloseAnn ~ AgeCent_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appAvgWide)

AIC(closeAnnMod, closeAnnModSq, closeAnnModCu)

farAnnModSq <- lm(FarAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appAvgWide)
farAnnModCu <- lm(FarAnn ~ AgeCent_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appAvgWide)

AIC(farAnnMod, farAnnModSq, farAnnModCu)
```

## Reviewer Suggestion - Control for reactivity rating
Here we created an average reactivity score to use as a control for analyses assessing people's regulation abilities. This helps account for an individual's baseline reactivity in relation to how well they are able to regulate. 

```{r FarRatingsControllingforReact}
## Far Regression
farBehavResContCloseAvg <- lmer(Rating ~ AgeCent + AvgClose + (1 | fsid), data=appLongFar)  
summary(farBehavResContCloseAvg)

## Best fit? 
farBehavResContCloseAvgSQ <- lmer(Rating ~ AgeCent + AgeSq + AvgClose + (1 | fsid), data=appLongFar)
farBehavResContCloseAvgCu <- lmer(Rating ~ AgeCent + AgeSq + AgeCu + AvgClose + (1 | fsid), data=appLongFar)

AIC(farBehavResContCloseAvg, farBehavResContCloseAvgSQ, farBehavResContCloseAvgCu)

## Is there a significant difference between the model with reactivity and the model without? 
anova(farBehav, farBehavResContCloseAvg)
## Linear fit still better
```

