---
title: "Regulation ROI Analysis"
author: "Rebecca Martin"
date: "6/24/2018"
output: 
    github_document:
        df_print: 'kable'
        toc: true
        dev: png
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---

Note: this is not a final version and should be cleaned and proofread.

## Settings

```{r settings}
knitr::opts_chunk$set(cache=TRUE)
```

```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
figureDir <- file.path(root, 'figures')
```

## Packages

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(bmlm)
library(arm)
```

## Read in data

```{r readData}
## Behavioral
appAvgLong <- read.table(file.path(dataDir,"app_avg_long.txt"), header=TRUE, sep="\t") ## for graphing 
appAvgWide <- read.table(file.path(dataDir,"app_avg_wide.txt"), header=TRUE, sep="\t")
demographicsLong <- read.table(file.path(dataDir,"demographicsLong.txt"), header=TRUE, sep="\t")
appBehavLongRaw <- read.table(file.path(dataDir,"app_behav_long.txt"), header=TRUE, sep="\t")

## Far ROI
far2TP <- read.table(file.path(dataDir, "far_2TP_combined_reduced.txt"), header=TRUE, sep="\t")
farRates <- read.table(file.path(dataDir, "farRates_reduced.txt"), header=TRUE, sep="\t")
```

## Merge ROI data with behavioral data and add age terms

```{r Merge}
appAvgLongROIs <- merge(appAvgLong, far2TP, by=c("fsid", "Phase"))

appAvgLongROIs$AgeCent <- appAvgLongROIs$Age - mean(appAvgLongROIs$Age)
appAvgLongROIs$AgeCentSq <- appAvgLongROIs$AgeCent*appAvgLongROIs$AgeCent
appAvgLongROIs$AgeCentCu <- appAvgLongROIs$AgeCent*appAvgLongROIs$AgeCent*appAvgLongROIs$AgeCent

appAvgLongReduced <- appAvgLongROIs %>% dplyr::select(Reactivity=Close, Regulation=Far, Age, fsid, Phase, Gender, rACC=rostralanteriorcingulate_lh, dmPFC=superiorfrontal_rh, dlPFC=rostralmiddlefrontal_lh, vlPFC=parsopercularis_rh) %>% gather(key=ROI, value=Thickness, -fsid, -Age, -Phase, -Gender, -Reactivity, -Regulation)

appWideROIRates <- merge(appAvgWide,farRates, by="fsid")
```

## Prep Graphs

```{r, make_theme, echo=FALSE, results='hide', message=FALSE}

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'), #color="black"
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        panel.grid.major=element_line(color="transparent"),
                        axis.title.x = element_text(size=24,face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16, face="bold"),
                        strip.text.x = element_text(size = 16, face="bold"),
                        legend.title = element_text(face="bold"),
                        axis.line.x=element_line(color = 'black'), 
                        axis.line.y=element_line(color = 'black'))
```

# Cortical ROIs

## Plot GLM clusters

```{r plotGLM}
ggplot(appAvgLongReduced, aes(x=Age, y=Thickness)) +
    geom_line(aes(y=Thickness, group=fsid), alpha=.5, size=.75) + 
    geom_point(aes(y=Thickness), size=1, alpha=.5) +
    geom_smooth(method='lm', color="black", ) +
    facet_wrap(~ROI, ncol=2) + 
    beckys.theme.conference +
    #theme_bw() +
    ylab("Cortical Thickness (mm)") +
    xlim(5,26) +
    #ylim(0,4) +
    scale_color_brewer(palette="Set1") +     scale_fill_brewer(palette="Set1") +
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", legend.title=element_blank(), strip.text.y = element_text(size = 14, face="bold"),
                        strip.text.x = element_text(size = 14, face="bold"),)

#ggsave("figures/AgeROI.pdf", width=7, height=5, dpi=300)
#ggsave("figures/AgeROIDiss.pdf", width=7, height=5, dpi=300)
```

## Cortical cluster statistics

### What is the shape of change in these ROIs? 

#### RACC
```{r corticalStatsrAcc}
summary(nullModrAcc <- lmer(rostralanteriorcingulate_lh ~ 1 + (1|fsid), data=appAvgLongROIs))
summary(linModrAcc <- lmer(rostralanteriorcingulate_lh ~ AgeCent + (1|fsid), data=appAvgLongROIs))
summary(quadModrAcc <- lmer(rostralanteriorcingulate_lh ~ AgeCent + AgeCentSq + (1|fsid), data=appAvgLongROIs))
summary(cubModrAcc <- lmer(rostralanteriorcingulate_lh ~ AgeCent + AgeCentSq + AgeCentCu + (1|fsid), data=appAvgLongROIs))
AIC(nullModrAcc, linModrAcc, quadModrAcc, cubModrAcc)
```

#### dmPFC  
```{r corticalStatsdmPFC}
summary(nullModdmPFC <- lmer(superiorfrontal_rh ~ 1 + (1|fsid), data=appAvgLongROIs))
summary(linModdmPFC <- lmer(superiorfrontal_rh ~ AgeCent + (1|fsid), data=appAvgLongROIs))
summary(quadModdmPFC <- lmer(superiorfrontal_rh ~ AgeCent + AgeCentSq + (1|fsid), data=appAvgLongROIs))
summary(cubModdmPFC <- lmer(superiorfrontal_rh ~ AgeCent + AgeCentSq + AgeCentCu + (1|fsid), data=appAvgLongROIs))
AIC(nullModdmPFC, linModdmPFC, quadModdmPFC, cubModdmPFC)
```

#### dlPFC 
```{r corticalStatsdlPFC}
summary(nullModdlPFC <- lmer(rostralmiddlefrontal_lh ~ 1 + (1|fsid), data=appAvgLongROIs))
summary(linModdlPFC <- lmer(rostralmiddlefrontal_lh ~ AgeCent + (1|fsid), data=appAvgLongROIs))
summary(quadModdlPFC <- lmer(rostralmiddlefrontal_lh ~ AgeCent + AgeCentSq + (1|fsid), data=appAvgLongROIs))
summary(cubModdlPFC <- lmer(rostralmiddlefrontal_lh ~ AgeCent + AgeCentSq + AgeCentCu + (1|fsid), data=appAvgLongROIs))
AIC(nullModdlPFC, linModdlPFC, quadModdlPFC, cubModdlPFC)
```

#### vlPFC 
```{r corticalStatsvlPFC}
summary(nullModvlPFC <- lmer(parsopercularis_rh ~ 1 + (1|fsid), data=appAvgLongROIs))
summary(linModvlPFC <- lmer(parsopercularis_rh ~ AgeCent + (1|fsid), data=appAvgLongROIs))
summary(quadModvlPFC <- lmer(parsopercularis_rh ~ AgeCent + AgeCentSq + (1|fsid), data=appAvgLongROIs))
summary(cubModvlPFC <- lmer(parsopercularis_rh ~ AgeCent + AgeCentSq + AgeCentCu + (1|fsid), data=appAvgLongROIs))
AIC(nullModvlPFC, linModvlPFC, quadModvlPFC, cubModvlPFC)
```

### Rates of change 

## Does change in thickness predict change in behavior? 

#### rACC
```{r}
## Thickness and behav rate change
summary(changethickbehav <- lm(FarAnn ~ rostralanteriorcingulate_lh_diffAnn, data=appWideROIRates))

## Age and thickness rate change? 
summary(changethickAge <- lm(rostralanteriorcingulate_lh_diffAnn ~ Age_T1, data=appWideROIRates))

### Age X Rate interactions on behavior?
summary(changeInt <- lm(FarAnn ~  rostralanteriorcingulate_lh_diffAnn*AgeCent_T1, data=appWideROIRates))
```

#### dmPFC
```{r}
## Thickness and behav rate change
summary(changethickbehav <- lm(FarAnn ~ superiorfrontal_rh_diffAnn, data=appWideROIRates))

## Age and thickness rate change? 
summary(changethickAge <- lm(superiorfrontal_rh_diffAnn ~ Age_T1, data=appWideROIRates))

### Age X Rate interactions on behavior?
summary(changeInt <- lm(FarAnn ~  superiorfrontal_rh_diffAnn*AgeCent_T1, data=appWideROIRates))
```

#### dlPFC
```{r}
## Thickness and behav rate change
summary(changethickbehav <- lm(FarAnn ~ rostralmiddlefrontal_lh_diffAnn, data=appWideROIRates))

## Age and thickness rate change? 
summary(changethickAge <- lm(rostralmiddlefrontal_lh_diffAnn ~ Age_T1, data=appWideROIRates))

### Age X Rate interactions on behavior?
summary(changeInt <- lm(FarAnn ~  rostralmiddlefrontal_lh_diffAnn*AgeCent_T1, data=appWideROIRates))
```

#### vlPFC
```{r}
## Thickness and behav rate change
summary(changethickbehav <- lm(FarAnn ~ parsopercularis_rh_diffAnn, data=appWideROIRates))

## Age and thickness rate change? 
summary(changethickAge <- lm(parsopercularis_rh_diffAnn ~ Age_T1, data=appWideROIRates))

### Age X Rate interactions on behavior?
summary(changeInt <- lm(FarAnn ~  parsopercularis_rh_diffAnn*AgeCent_T1, data=appWideROIRates))
```

#### What is the shape of the rate changes? 
```{r}
## rACC
rACCchangethickAgeNull <- lm(rostralanteriorcingulate_lh_diffAnn ~ 1, data=appWideROIRates)
rACCchangethickAgeLin <- lm(rostralanteriorcingulate_lh_diffAnn ~ AgeCent_T1, data=appWideROIRates)
rACCchangethickAgeSq <- lm(rostralanteriorcingulate_lh_diffAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appWideROIRates)
rACCchangethickAgeCu <- lm(rostralanteriorcingulate_lh_diffAnn ~ Age_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appWideROIRates)

AIC(rACCchangethickAgeNull, rACCchangethickAgeLin, rACCchangethickAgeSq, rACCchangethickAgeCu)

## dmPFC
dmPFCchangethickAgeNull <- lm(superiorfrontal_rh_diffAnn ~ 1, data=appWideROIRates)
dmPFCchangethickAgeLin <- lm(superiorfrontal_rh_diffAnn ~ AgeCent_T1, data=appWideROIRates)
dmPFCchangethickAgeSq <- lm(superiorfrontal_rh_diffAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appWideROIRates)
dmPFCchangethickAgeCu <- lm(superiorfrontal_rh_diffAnn ~ Age_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appWideROIRates)

AIC(dmPFCchangethickAgeNull, dmPFCchangethickAgeLin, dmPFCchangethickAgeSq, dmPFCchangethickAgeCu)

## dlPFC
dlPFCchangethickAgeNull <- lm(rostralmiddlefrontal_lh_diffAnn ~ 1, data=appWideROIRates)
dlPFCchangethickAgeLin <- lm(rostralmiddlefrontal_lh_diffAnn ~ AgeCent_T1, data=appWideROIRates)
dlPFCchangethickAgeSq <- lm(rostralmiddlefrontal_lh_diffAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appWideROIRates)
dlPFCchangethickAgeCu <- lm(rostralmiddlefrontal_lh_diffAnn ~ Age_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appWideROIRates)

AIC(dlPFCchangethickAgeNull, dlPFCchangethickAgeLin, dlPFCchangethickAgeSq, dlPFCchangethickAgeCu)

## vlPFC
vlPFCchangethickAgeNull <- lm(parsopercularis_rh_diffAnn ~ 1, data=appWideROIRates)
vlPFCchangethickAgeLin <- lm(parsopercularis_rh_diffAnn ~ AgeCent_T1, data=appWideROIRates)
vlPFCchangethickAgeSq <- lm(parsopercularis_rh_diffAnn ~ AgeCent_T1 + AgedCentSq_T1, data=appWideROIRates)
vlPFCchangethickAgeCu <- lm(parsopercularis_rh_diffAnn ~ AgeCent_T1 + AgedCentSq_T1 + AgedCentCu_T1, data=appWideROIRates)

AIC(vlPFCchangethickAgeNull, vlPFCchangethickAgeLin, vlPFCchangethickAgeSq, vlPFCchangethickAgeCu)
```

#### Plot Rates of Change by ROI
```{r}
AparcRename <- appWideROIRates %>% 
    dplyr::select(fsid, Age_T1, dmPFC=superiorfrontal_rh_diffAnn,
                  dlPFC=rostralmiddlefrontal_lh_diffAnn,
                  vlPFC=parsopercularis_rh_diffAnn,
                  rACC=rostralanteriorcingulate_lh_diffAnn) %>% 
    gather(key=ROI, value=Thickness, -fsid, -Age_T1)



ggplot(AparcRename, aes(x=Age_T1, y=Thickness)) +
    geom_point(aes(y=Thickness), shape=1, size=1, alpha=.4) +
    geom_smooth(method='lm', color="black") + # linear change
    #geom_smooth(color="black") +  # let's look nonlinear
    geom_hline(yintercept = 0) +
    facet_wrap(~ROI, ncol=6) + 
    beckys.theme.conference +
    #theme_bw() +
    ylab("Annualized Thickness Change") +
    xlab("Age at T1") +
    xlim(5, 26) +
    ylim(-.2,.2)
    

#ggsave("figures/farRateROI4RandR.pdf", width=10, height=6, dpi=300)
```

#### Do Rates of Change in behav correlate with rates of change in neural regions? 
```{r}
summary(rACCchangethickBehav <- lm(rostralanteriorcingulate_lh_diffAnn ~ FarAnn, data=appWideROIRates))
summary(dmPFCchangethickBehav <- lm(superiorfrontal_rh_diffAnn ~ FarAnn, data=appWideROIRates))
summary(dlPFCchangethickBehav <- lm(rostralmiddlefrontal_lh_diffAnn ~ FarAnn, data=appWideROIRates))
summary(vlPFCchangethickBehav <- lm(parsopercularis_rh_diffAnn ~ FarAnn, data=appWideROIRates))

# Nope rates of change in behav don't relate to rates of change in structure

## What about controlling for age? 
summary(rACCchangethickBehavAge <- lm(rostralanteriorcingulate_lh_diffAnn ~ FarAnn + AgeCent_T1, data=appWideROIRates))
summary(dmPFCchangethickBehavAge <- lm(superiorfrontal_rh_diffAnn ~ FarAnn + AgeCent_T1, data=appWideROIRates))
summary(dlPFCchangethickBehavAge <- lm(rostralmiddlefrontal_lh_diffAnn ~ FarAnn + AgeCent_T1, data=appWideROIRates))
summary(vlPFCchangethickBehavAge <- lm(parsopercularis_rh_diffAnn ~ FarAnn + AgeCent_T1, data=appWideROIRates))

# Nope. 

## Interaction with age? 
## What about controlling for age? 
summary(rACCchangethickBehaXvAge <- lm(rostralanteriorcingulate_lh_diffAnn ~ FarAnn*AgeCent_T1, data=appWideROIRates))
summary(dmPFCchangethickBehavXAge <- lm(superiorfrontal_rh_diffAnn ~ FarAnn*AgeCent_T1, data=appWideROIRates))
summary(dlPFCchangethickBehavXAge <- lm(rostralmiddlefrontal_lh_diffAnn ~ FarAnn*AgeCent_T1, data=appWideROIRates))
summary(vlPFCchangethickBehavXAge <- lm(parsopercularis_rh_diffAnn ~ FarAnn*AgeCent_T1, data=appWideROIRates))
```

