---
title: "Subcortical Analysis"
author: "Rebecca Martin"
date: "6/24/2018"
output: 
    github_document:
        df_print: 'paged'
        toc: true
        dev: png
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: true
        code_download: true
        self_contained: true
        code_folding: 'hide'
---

Note: this script needs to be proofread and cleaned up and is not a final version


## Settings

```{r settings}
knitr::opts_chunk$set(cache=TRUE)
```

```{r setDirs}
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'code')
figureDir <- file.path(root, 'figures')
```

## Packages

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(bmlm)
library(arm)
```

## Read in data

```{r readData}
## Behavioral
appAvgLong <- read.table(file.path(dataDir,"app_avg_long.txt"), header=TRUE, sep="\t") ## for graphing 
appAvgWide <- read.table(file.path(dataDir,"app_avg_wide.txt"), header=TRUE, sep="\t")
demographicsLong <- read.table(file.path(dataDir,"demographicsLong.txt"), header=TRUE, sep="\t")
appBehavLongRaw <- read.table(file.path(dataDir,"app_behav_long.txt"), header=TRUE, sep="\t")

# Subcortical ROIs
asegLong <- read.table(file.path(dataDir,"asegLong.txt"), header=TRUE, sep="\t")
asegRate <- read.table(file.path(dataDir, "appAsegRate.txt"), header=TRUE, sep="\t")
aseg2TPWide <- read.table(file.path(dataDir, "aseg2TPwide.txt"), header=TRUE, sep="\t")
```

## Merge ROI data with behavioral data, add age terms, and center (zscore) subcortical values

```{r Merge}
## Merge data
appLongAll <- merge(appBehavLongRaw, demographicsLong, by=c('ID', 'Phase'))
asegLongPlusBehav <- merge(appLongAll, asegLong, by=c('ID', 'Phase'))
asegLongPlusBehav2TP <- merge(appLongAll, asegLong, by=c('ID', 'Phase'))
aseg2TPbehav <- merge(appAvgLong, asegLong, by=c('ID', 'Phase'))
asegRatePlusBehav <- merge(appAvgWide, asegRate, by=c("ID","fsid"))
aseg2TPWideBehav <- merge(appAvgWide, aseg2TPWide, by=c('fsid'))

## Age Terms
aseg2TPbehav$AgeCent <- scale(aseg2TPbehav$Age, scale=FALSE)
aseg2TPbehav$AgeCent <- as.numeric(aseg2TPbehav$AgeCent)
aseg2TPbehav$AgeCentSq <- aseg2TPbehav$AgeCent*aseg2TPbehav$AgeCent
aseg2TPbehav$AgeCentCu <- aseg2TPbehav$AgeCent*aseg2TPbehav$AgeCent*aseg2TPbehav$AgeCent

asegLongPlusBehav$AgeCent <- scale(asegLongPlusBehav$Age, scale=FALSE)
asegLongPlusBehav$AgeCent <- as.numeric(asegLongPlusBehav$AgeCent)
asegLongPlusBehav$AgeCentSq <- asegLongPlusBehav$AgeCent*asegLongPlusBehav$AgeCent
asegLongPlusBehav$AgeCentCu <- asegLongPlusBehav$AgeCent*asegLongPlusBehav$AgeCent*asegLongPlusBehav$AgeCent

## Scale Volumes
aseg2TPbehav$RHNAccScaled <- scale(aseg2TPbehav$Right.Accumbens.area)
aseg2TPbehav$LHNAccScaled <- scale(aseg2TPbehav$Left.Accumbens.area)
aseg2TPbehav$ETivCrossScaled <- scale(aseg2TPbehav$ETivCross)
aseg2TPbehav$LHWBVScaled <- scale(aseg2TPbehav$lhCortexVol)
aseg2TPbehav$RHWBVScaled <- scale(aseg2TPbehav$rhCortexVol)
aseg2TPbehav$RHNAccScaled <- as.numeric(aseg2TPbehav$RHNAccScaled)
aseg2TPbehav$LHNAccScaled <- as.numeric(aseg2TPbehav$LHNAccScaled)
aseg2TPbehav$ETivCrossScaled <- as.numeric(aseg2TPbehav$ETivCrossScaled)
aseg2TPbehav$LHWBVScaled <- as.numeric(aseg2TPbehav$LHWBVScaled)
aseg2TPbehav$RHWBVScaled <- as.numeric(aseg2TPbehav$RHWBVScaled)

asegLongPlusBehav$RHNAccScaled <- scale(asegLongPlusBehav$Right.Accumbens.area)
asegLongPlusBehav$LHNAccScaled <- scale(asegLongPlusBehav$Left.Accumbens.area)
asegLongPlusBehav$ETivCrossScaled <- scale(asegLongPlusBehav$ETivCross)
asegLongPlusBehav$LHWBVScaled <- scale(asegLongPlusBehav$lhCortexVol)
asegLongPlusBehav$RHWBVScaled <- scale(asegLongPlusBehav$rhCortexVol)
asegLongPlusBehav$RHNAccScaled <- as.numeric(asegLongPlusBehav$RHNAccScaled)
asegLongPlusBehav$LHNAccScaled <- as.numeric(asegLongPlusBehav$LHNAccScaled)
asegLongPlusBehav$ETivCrossScaled <- as.numeric(asegLongPlusBehav$ETivCrossScaled)
asegLongPlusBehav$LHWBVScaled <- as.numeric(asegLongPlusBehav$LHWBVScaled)
asegLongPlusBehav$RHWBVScaled <- as.numeric(asegLongPlusBehav$RHWBVScaled)
```

## Make subsets
```{r}
asegLongPlusBehavClose <- asegLongPlusBehav %>% dplyr::filter(Type=="Close")
asegLongPlusBehavFar <- asegLongPlusBehav %>% dplyr::filter(Type=="Far")
```

## Prep Graphs

```{r, make_theme, echo=FALSE, results='hide', message=FALSE}

beckys.theme.conference = theme(panel.background = element_rect(fill='transparent'), #color="black"
                        axis.line = element_line(color='black'),
                        panel.grid.minor = element_line(color='transparent'),
                        panel.grid.major=element_line(color="transparent"),
                        axis.title.x = element_text(size=24,face = "bold"),
                        axis.title.y = element_text(size=24, vjust=1, face = "bold"),
                        axis.text.x = element_text(size=16, colour="black"),
                        axis.text.y = element_text(size=16, colour="black"),
                        legend.text=element_text(size=16),
                        strip.text.y = element_text(size = 16, face="bold"),
                        strip.text.x = element_text(size = 16, face="bold"),
                        legend.title = element_text(face="bold"),
                        axis.line.x=element_line(color = 'black'), 
                        axis.line.y=element_line(color = 'black'))
```

# Subcortical ROIs

## Question 1: Volume
Does NAcc volume predict reactivity or regulation (accounting for gender, then accounting for ICV, then accounting for WBV)?

```{r}
## Close
summary(NAccLHClose <- lmer(LHNAccScaled ~ AgeCent + (1 | ID), data=aseg2TPbehav))

summary(NAccRHClose <- lmer(RHNAccScaled ~ AgeCent + (1 | ID), data=aseg2TPbehav))

summary(NAccLHClose <- lmer(Close ~ LHNAccScaled + (1 | ID), data=aseg2TPbehav))

summary(NAccRHClose <- lmer(Close ~ RHNAccScaled + (1 | ID), data=aseg2TPbehav))

## Far
summary(NAccLHFar <- lmer(Far ~ LHNAccScaled + (1 | ID), data=aseg2TPbehav))

summary(NAccRHFar <- lmer(Far ~ RHNAccScaled + (1 | ID), data=aseg2TPbehav))

## Close X Age Interaction
summary(NAccLHCloseInt <- lmer(Close ~ LHNAccScaled*AgeCent + Gender + (1 | ID), data=aseg2TPbehav))

summary(NAccRHCloseInt <- lmer(Close ~ RHNAccScaled*AgeCent + Gender + (1 | ID), data=aseg2TPbehav))

### Not really. 
## Age predicts NAcc volume
## Age*NAcc does not predict close scoress. Controlling for Gender and ETivCross doesn't help. 
```

## Question 2: Rates of change
Does change in volume predict change in rating? Is there an interaction with age? 

```{r}
## Close
## Age and reactivity rate change? 
summary(lm(CloseAnn ~ Age_T1, data=asegRatePlusBehav))

## Far
summary(lm(FarAnn ~ Age_T1, data=asegRatePlusBehav))

## Age X NAcc rate change interactions on behavior?
summary(lm(CloseAnn ~  Right.Accumbens.area*AgeCent_T1 + Gender, data=asegRatePlusBehav))

## Far
summary(lm(FarAnn ~ Right.Accumbens.area*AgeCent_T1 + Gender, data=asegRatePlusBehav))
```

## Question 3: Weight Gain and NAcc 
Are people with smaller NAcc volumes more likely to increase in weight at time 2?
```{r}
summary(NAccBMILH <- lm(BMIPerc_T2 ~ BMIPerc_T1*Left.Accumbens.area + Age_T1, data=aseg2TPWideBehav))

summary(NAccBMIRH <- lm(BMIPerc_T2 ~ Right.Accumbens.area*BMIPerc_T1 + Age_T1 + ETivCross, data=aseg2TPWideBehav))
### this interaction is significant, particularly for right hemisphere. holds up when controlling for age and interaction with age also significant

## how about does BMI predict accumbens volume at T2?
summary(NAccBMI2 <- lm(Right.Accumbens.area.1 ~ BMIPerc_T1*Right.Accumbens.area + Age_T1 + ETivCross, data=aseg2TPWideBehav))

## does NAcc correlate with BMI Perc controlling for age
summary(NAccCorr <- lm(Right.Accumbens.area ~ BMIPerc_T1 + Age_T1, data=aseg2TPWideBehav))
### Nope!
```

## Prep data to look at NAcc and BMI Percentile
```{r}
## Make subset for volume
BMIPercPlot <- aseg2TPWideBehav %>% dplyr::select(Right.Accumbens.area, Left.Accumbens.area, BMIPerc_T1, BMIPerc_T2, BMIGroup_T1_Reduced, BMIGroup_T2_Reduced, Age_T1, ETivCross, TimeElapsed)

## Make subsets for rate changes
BMIPercPlotRate <- asegRatePlusBehav %>% dplyr::select(Right.Accumbens.area, Left.Accumbens.area, BMIPerc_T1, BMIPerc_T2, Age_T1)

BMIPercPlotRate$BMIChange <- BMIPercPlotRate$BMIPerc_T1 - BMIPercPlotRate$BMIPerc_T2

BMIPercPlotRate <- BMIPercPlotRate %>% dplyr::mutate(WeightGroup=ifelse(BMIPerc_T1 < 85, 'Healthy', 'Overweight'))

BMIPercPlotRateNoNAs <- BMIPercPlotRate %>% dplyr::filter(complete.cases(.))

BMIPercPlotRate <- asegRatePlusBehav %>% dplyr::select(Right.Accumbens.area, Left.Accumbens.area, BMIPerc_T1, BMIPerc_T2, Age_T1)

BMIPercPlotRate$BMIChange <- BMIPercPlotRate$BMIPerc_T1 - BMIPercPlotRate$BMIPerc_T2

BMIPercPlotRate <- BMIPercPlotRate %>% dplyr::mutate(WeightGroup=ifelse(BMIPerc_T1 < 85, 'Healthy', 'Overweight'))

BMIPercPlotRateNoNAs <- BMIPercPlotRate %>% dplyr::filter(complete.cases(.))

## Remove NAs
BMIPercPlotNoNAs <- BMIPercPlot %>% dplyr::filter(complete.cases(.))
NAccBMIRH <- lm(BMIPerc_T2 ~ Right.Accumbens.area*BMIPerc_T1 + Age_T1 + ETivCross, data=BMIPercPlotNoNAs, na.action = na.exclude)

## make BMI change score
BMIPercPlotNoNAs$BMIChangeAnn <- (BMIPercPlotNoNAs$BMIPerc_T2 - BMIPercPlotNoNAs$BMIPerc_T1)/BMIPercPlotNoNAs$TimeElapsed

### Center for interactions
BMIPercPlotNoNAs$RHNAccScaled <- scale(BMIPercPlotNoNAs$Right.Accumbens.area)
BMIPercPlotNoNAs$LHNAccScaled <- scale(BMIPercPlotNoNAs$Left.Accumbens.area)
BMIPercPlotNoNAs$ETivCrossScaled <- scale(BMIPercPlotNoNAs$ETivCross)
BMIPercPlotNoNAs$BMIPerc_T1_Scaled <- scale(BMIPercPlotNoNAs$BMIPerc_T1, scale=FALSE)

BMIPercPlotNoNAs$RHNAccScaled <- as.numeric(BMIPercPlotNoNAs$RHNAccScaled)
BMIPercPlotNoNAs$LHNAccScaled <- as.numeric(BMIPercPlotNoNAs$LHNAccScaled)
BMIPercPlotNoNAs$ETivCrossScaled <- as.numeric(BMIPercPlotNoNAs$ETivCrossScaled)
BMIPercPlotNoNAs$BMIPerc_T1_Scaled <- as.numeric(BMIPercPlotNoNAs$BMIPerc_T1_Scaled)

## make low/high distinction for BMI
BMIPercPlotNoNAs <- BMIPercPlotNoNAs %>% dplyr::mutate(Type=ifelse(BMIPerc_T1 < 85, 'Healthy', 'Overweight'))
```

Question 4: Volume change and BMI
```{r}
summary(NAccBMIRHChange <- lm(BMIChangeAnn ~ Right.Accumbens.area*BMIPerc_T1 + ETivCross, data=BMIPercPlotNoNAs, na.action = na.exclude))
#### I think I can report on this one... There are only 24 subs and I think that there may be two outliers driving the effects. Need to look at cook's distance I think. 

## Does NAcc at T1 predict increases in BMI at time 2? 
summary(bmichange <- lm(BMIChangeAnn ~ Right.Accumbens.area, data=BMIPercPlotNoNAs))
## nope not by itself

### How about controlling for BMI
summary(bmichange <- lm(BMIChangeAnn ~ Right.Accumbens.area + BMIPerc_T1, data=BMIPercPlotNoNAs))
## Closer

## Interaction??
summary(bmichange <- lm(BMIChangeAnn ~ Right.Accumbens.area*BMIPerc_T1, data=BMIPercPlotNoNAs))

summary(bmichange <- lm(BMIChangeAnn ~ Right.Accumbens.area*BMIGroup_T1_Reduced, data=BMIPercPlotNoNAs))

summary(NAccBMIRHChangeScaled <- lm(BMIChangeAnn ~ LHNAccScaled*BMIPerc_T1_Scaled + ETivCrossScaled, data=BMIPercPlotNoNAs, na.action = na.exclude))

####
NAccBMIRHChange <- lm(BMIChangeAnn ~ RHNAccScaled*BMIPerc_T1_Scaled + ETivCross, data=BMIPercPlotNoNAs, na.action = na.exclude)
summary(NAccBMIRHChange)

NAccBMIRHChangeL <- lm(BMIChangeAnn ~ LHNAccScaled*BMIPerc_T1_Scaled + ETivCross, data=BMIPercPlotNoNAs, na.action = na.exclude)
summary(NAccBMIRHChangeL)
####

## Let's look multilevel
NAccBMI_ML <- lmer(BMIPerc ~ LHNAccScaled + ETivCrossScaled + (1|ID), data=asegLongPlusBehav)

aseg2TPbehav <- aseg2TPbehav %>% mutate(WeightStatus=ifelse(BMIPerc < 85, 0, 1))

## Get residuals for plotting
BMIPercPlotNoNAs$changeresid <- resid(NAccBMIRHChange)
BMIPercPlotNoNAs$residval <- resid(NAccBMIRH)

BMIPercPlotNoNAs$changeresid <- as.numeric(BMIPercPlotNoNAs$changeresid)
BMIPercPlotNoNAs$residval <- as.numeric(BMIPercPlotNoNAs$residval)
```

BMI Percentile and VS
```{r}
## try with two tps 
summary(NAccBMI_ML2 <- lmer(LHNAccScaled ~ BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav)) #asegLongPlusBehav
summary(NAccBMI_ML2 <- lmer(RHNAccScaled~ BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))

summary(NAccBMIPerc_ML2 <- lmer(LHNAccScaled ~ BMIPerc + (1|ID), data=aseg2TPbehav)) #asegLongPlusBehav
summary(NAccBMIPerc_ML2 <- lmer(RHNAccScaled ~ BMIPerc + (1|ID), data=aseg2TPbehav))

summary(NAccBMI_ML2 <- lmer(LHNAccScaled ~ BMIGroupReduced + (1|ID), data=aseg2TPbehav)) #asegLongPlusBehav
summary(NAccBMI_ML2 <- lmer(RHNAccScaled ~ BMIGroupReduced + (1|ID), data=aseg2TPbehav)) 

summary(NAccBMI_ML2 <- lmer(LHNAccScaled ~ BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav)) #asegLongPlusBehav
summary(NAccBMI_ML2 <- lmer(RHNAccScaled ~ BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))

summary(ETiv <- lmer(ETivCrossScaled ~ BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav)) 

#asegLongPlusBehav
##### ICV is smaller in this sample of participants too...

NAccBMI_ML3 <- glmer(WeightStatus~ LHNAccScaled + ETivCrossScaled + (1|ID), data=aseg2TPbehav, family="binomial")

## Look by group
NAccBMIRHChange <- lm(BMIChangeAnn ~ Right.Accumbens.area*Type, data=BMIPercPlotNoNAs, na.action = na.exclude)
```

Does group predict size?
```{r}
NAccBMI <- lm(Right.Accumbens.area ~ Type, data=BMIPercPlotNoNAs, na.action = na.exclude)
```
Yes!!! Healthy subs have bigger accumbens (when I look by group)
```{r}
NAccBMI <- lm(Left.Accumbens.area.1 ~ BMIGroup_T1, data=aseg2TPWideBehav, na.action = na.exclude)
```
BMI group at T1 predict accumbens volume at t2

```{r}
NAccBMI2 <- lm(Left.Accumbens.area ~  BMIGroup_T1, data=aseg2TPWideBehav, na.action = na.exclude)
```
Ok I think I can say something about overweight people having smaller NAccs at both T1 and T2. BMI group at T1 predicts accumbens volume at T2 (and T1). Basically, when you are overweight, you are more likely to have a smaller NAcc. There doesn't seem to be an effect of change in BMI status or Accumbens volume. Treating subs as groups so I can include adults helps. Also, there is no effect of age. This seems to be an age independent effect. This paper replicates the results I'm seeing: Pannacciulli, N., Del Parigi, A., Chen, K., Le, D. S. N. T., Reiman, E. M., & Tataranni, P. A. (2006). Brain abnormalities in human obesity: A voxel-based morphometric study. NeuroImage, 31(4), 1419–1425. https://doi.org/10.1016/j.neuroimage.2006.01.047

```{r}
summary(NAccBMI4 <- lm(ETivCross ~  BMIGroup_T1, data=aseg2TPWideBehav, na.action = na.exclude))
```
also found obesity related to low brain volume, which replicates this study: Raji, C. A., Ho, A. J., Parikshak, N. N., Becker, J. T., Lopez, O. L., Kuller, L. H., … Thompson, P. M. (2010). Brain structure and obesity. Human Brain Mapping, 31(3), 353–364. https://doi.org/10.1002/hbm.20870, and this one: Taki, Y., Kinomura, S., Sato, K., Inoue, K., Goto, R., Okada, K., … Fukuda, H. (2008). Relationship Between Body Mass Index and Gray Matter Volume in 1,428 Healthy Individuals. Obesity, 16(1), 119–124. https://doi.org/10.1038/oby.2007.4

The next step is to look at craving and regulation and NAcc volume...
```{r}
NAccCloseBMI <- lm(Left.Accumbens.area ~  BMIGroup_T1*p1Close + Age_T1, data=aseg2TPWideBehav, na.action = na.exclude)
```
Yes there is an effect! Effect remains but weakens when I include ETivCross. Adding age as a control helps. This seems to reverse and be more predictive for underweight individuals.

```{r}
summary(NAccCloseBMI2 <- lm(p1Close ~  BMIGroup_T1_Reduced*Left.Accumbens.area + ETivCross, data=aseg2TPWideBehav, na.action = na.exclude))
```
EFfect is weaker when I look at it this way. There is an effect for close but not far.. It gets stronger with ETivCross though. 

```{r}
summary(NAccCloseBMI2 <- lm(p1Close ~  BMI_T1*Left.Accumbens.area + ETivCross, data=aseg2TPWideBehav, na.action = na.exclude))

## What about change?
aseg2TPWideBehav$LeftNAccChange <- aseg2TPWideBehav$Left.Accumbens.area - aseg2TPWideBehav$Left.Accumbens.area.1
aseg2TPWideBehav$RightNAccChange <- aseg2TPWideBehav$Right.Accumbens.area - aseg2TPWideBehav$Right.Accumbens.area.1

NAccBMIChangeClose <- lm(FarDiff ~ RightNAccChange*BMIGroup_T1 + TimeElapsed, data=aseg2TPWideBehav, na.action = na.exclude)
summary(NAccBMIChangeClose)
```
nope, no effect for Close or Far and change...

```{r}
## what about accumbens change??? Does bmi change relate to accumbens change? 
BMIPercPlotRate <- asegRatePlusBehav %>% dplyr::select(Right.Accumbens.area, Left.Accumbens.area, BMIPerc_T1, BMIPerc_T2, Age_T1)

BMIPercPlotRate$BMIChange <- BMIPercPlotRate$BMIPerc_T1 - BMIPercPlotRate$BMIPerc_T2

BMIPercPlotRate <- BMIPercPlotRate %>% dplyr::mutate(WeightGroup=ifelse(BMIPerc_T1 < 85, 'Healthy', 'Overweight'))

BMIPercPlotRateNoNAs <- BMIPercPlotRate %>% dplyr::filter(complete.cases(.))

NAccBMI_RateChange <- lm(BMIChange ~ Left.Accumbens.area*BMIPerc_T1, data=BMIPercPlotRateNoNAs)

summary(NAccBMI_RateChange)
```
No effects here that I can find.

## Plots
```{r}
ggplot(BMIPercPlotNoNAs, aes(x=Right.Accumbens.area, y=BMIChangeAnn, color=Type)) +
    geom_point(aes(color=Type)) +
    geom_smooth(method="lm", se=FALSE)

ggplot(BMIPercPlotNoNAs, aes(x=Right.Accumbens.area, y=BMIChangeAnn)) +
    geom_point(aes(color=Type)) +
    geom_smooth(method="lm")


ggplot(BMIPercPlotNoNAs, aes(x=BMIPerc_T1, y=Right.Accumbens.area)) +
    geom_point(aes(color=Type)) +
    geom_smooth(method="lm")


## long plotting
aseg2TPbehav$ID <- as.character(aseg2TPbehav$ID)
aseg2TPbehav$Phase <- as.character(aseg2TPbehav$Phase)

bmi <- ggplot(aseg2TPbehav, aes(x=BMIPerc, y=Right.Accumbens.area)) + 
    geom_point(aes(group=ID, color=Phase), alpha=.5) +
    geom_line(aes(group=ID), color="#e41a1c", alpha=.5) + 
    beckys.theme.conference + 
    # theme(legend.position = "none") + 
    #ylab("Rating of Craving") + 
    #ylim(1,5) +
    geom_smooth(color='black', method=lm) 
    #ggtitle("Craving Decreases With Age")
bmi

```

## Plot VS and Age

merge lh and rh 
```{r}
asegBehavReduced <- aseg2TPbehav %>% dplyr::select(Reactivity=Close, Regulation=Far, Age, ID, Phase, Gender, LH=Left.Accumbens.area, RH=Right.Accumbens.area) %>% gather(key=hemi, value=Volume, -ID, -Reactivity, -Regulation, -Age, -Phase, -Gender)
```

Plot age and VS
```{r}
ggplot(asegBehavReduced, aes(x=Age, y=Volume)) +
    geom_point(aes(y=Volume), shape=1, size=1, alpha=.2) +
    geom_line(aes(y=Volume, group=ID), alpha=.2) + 
    geom_smooth(method='lm', color="black", ) +
    facet_wrap(~hemi) + 
    beckys.theme.conference +
    #theme_bw() +
    ylab("VS Volume (mm3)") + 
    xlim(5,26) +
    #ylim(0,4) +
    scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") 
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", #legend.title=element_blank(), strip.text.y = element_text(size = 14, face="bold"),
                        strip.text.x = element_text(size = 14, face="bold"),)

#ggsave("figures/VSAge.pdf", width=7, height=5, dpi=300)
```

Reactivity and VS
```{r}
ggplot(asegBehavReduced, aes(x=Volume, y=Reactivity)) +
    geom_point(aes(y=Reactivity, color=Gender), shape=1, size=1, alpha=.3) +
    geom_line(aes(y=Reactivity, group=ID, color=Gender), alpha=.3) + 
    geom_smooth(method='lm', color="black", ) +
    facet_wrap(~hemi) + 
    beckys.theme.conference +
    #theme_bw() +
    #ylab("VS Volume (mm3)") + 
    #xlim(1,5) +
    ylim(1,5) +
    scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") 
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", #legend.title=element_blank(), strip.text.y = element_text(size = 14, face="bold"),
                        strip.text.x = element_text(size = 14, face="bold"),)

#ggsave("BehavMainEffects.pdf", width=15, height=5, dpi=300)
```

Regulation and VS
```{r}
ggplot(asegBehavReduced, aes(x=Volume, y=Regulation)) +
    geom_point(aes(y=Regulation, color=Gender), shape=1, size=1, alpha=.3) +
    geom_line(aes(y=Regulation, group=ID, color=Gender), alpha=.3) + 
    geom_smooth(method='lm', color="black", ) +
    facet_wrap(~hemi) + 
    beckys.theme.conference +
    #theme_bw() +
    #ylab("VS Volume (mm3)") + 
    #xlim(1,5) +
    ylim(1,5) +
    scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") 
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", #legend.title=element_blank(), strip.text.y = element_text(size = 14, face="bold"),
                        strip.text.x = element_text(size = 14, face="bold"),)

#ggsave("BehavMainEffects.pdf", width=15, height=5, dpi=300)
```

Plot BMI Group and VS 
```{r}
ggplot(aseg2TPbehav, aes(x=BMIGroup, y=LHNAccScaled)) +
    geom_jitter(aes(y=LHNAccScaled, color=BMIGroup), width=.1) +
    #geom_line(aes(y=LHNAccScaled, group=ID, color=BMIGroup)) + 
    geom_smooth(method='lm', color="black") +
    beckys.theme.conference +
    #theme_bw() +
    #ylab("VS Volume (mm3)") + 
    #xlim(1,5) +
    #ylim(1,5) +
    #scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") 
    #scale_color_manual(values=c("#e41a1c", "#377eb8")) + 
    theme(legend.position="none", strip.text.x = element_text(size = 14, face="bold"),)

##### Plot averages here and average volume
aseg2TPbehav2 <- aseg2TPbehav %>% filter(BMIGroup!="NA") 

ggplot(aseg2TPbehav2, aes(x=BMIPerc, y=Left.Accumbens.area)) +
    geom_jitter(aes(y=Left.Accumbens.area, color=BMIGroup), width=.1) +
    #geom_line(aes(y=LHNAccScaled, group=ID, color=BMIGroup)) + 
    geom_smooth(method='lm', color="black") +
    ylab("Left VS Volume (mm3)") + 
    beckys.theme.conference 
```

Ok effect of BMI and NAcc on Behavior? 
```{r}
## BMI and Close?
summary(lmer(Close ~ BMIPerc + (1|ID), data=aseg2TPbehav)) # BMI perc show lower reactivity...

summary(lmer(Close ~ BMIGroupReduced + (1|ID), data=aseg2TPbehav)) 
summary(lmer(Far ~ BMIGroupReduced + (1|ID), data=aseg2TPbehav)) 

summary(lmer(Far ~ BMIPerc + (1|ID), data=aseg2TPbehav)) 
summary(lmer(Close ~ BMIPerc*AgeCent + (1|ID), data=aseg2TPbehav)) 
summary(lm(CloseAnn ~ BMIGroup_T1_Reduced*Left.Accumbens.area + AgeCent_T1, data=aseg2TPWideBehav))
summary(lmer(Close ~ LHNAccScaled + (1|ID), data=aseg2TPbehav))
summary(lm(Close ~ BMIGroupReduced*Right.Accumbens.area + AgeCent, data=aseg2TPbehav))

summary(closeInt <-  lmer(Close ~ BMIGroupReduced*LHNAccScaled + AgeCent + (1|ID), data=aseg2TPbehav))

residMod <- lmer(Close ~ AgeCent + (1|ID), data=aseg2TPbehav)
aseg2TPbehav$CloseAgeResid <- resid(residMod)
```

Best Fit models for age? 
```{r}
summary(NAccLHClose <- lmer(LHNAccScaled ~ AgeCent + LHWBVScaled + (1 | ID), data=aseg2TPbehav))
summary(NAccLHClose <- lmer(RHNAccScaled ~ AgeCent + RHWBVScaled + (1 | ID), data=aseg2TPbehav))

summary(NAccLHClose <- lmer(LHNAccScaled ~ BMIGroupReduced + LHWBVScaled + (1 | ID), data=aseg2TPbehav))
summary(NAccLHClose <- lmer(RHNAccScaled ~ BMIGroupReduced + RHWBVScaled + (1 | ID), data=aseg2TPbehav))

## Control for age
summary(NAccLHClose <- lmer(LHNAccScaled ~ BMIGroupReduced + LHWBVScaled + AgeCent + (1 | ID), data=aseg2TPbehav))
summary(NAccLHClose <- lmer(RHNAccScaled ~ BMIGroupReduced + RHWBVScaled + AgeCent + (1 | ID), data=aseg2TPbehav))

## Linear best fit...ETivCrossScaled, RHWBVScaled
```

Is there a relationship between whole brain volume and BMI Perc?? (Do heavier people have lower brain volumes overall?)
```{r wbv-BMIPerc}
summary(BMIGroupVolLH <- lmer(lhCortexVol ~BMIGroupReduced + (1|ID), data=aseg2TPbehav))
summary(BMIPercVolLH <- lmer(lhCortexVol ~BMIGroupReduced + (1|ID), data=aseg2TPbehav))

summary(BMIGroupVolRH <- lmer(rhCortexVol ~BMIGroupReduced + (1|ID), data=aseg2TPbehav))
summary(BMIPercVolRH <- lmer(rhCortexVol ~BMIGroupReduced + (1|ID), data=aseg2TPbehav))

## Control for Age
summary(BMIGroupVolLHAge <- lmer(lhCortexVol ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))
summary(BMIPercVolLHAge <- lmer(lhCortexVol ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))

summary(BMIGroupVolRHAge <- lmer(rhCortexVol ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))
summary(BMIPercVolRHAge <- lmer(rhCortexVol ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))
```

Look at this correcting for whole brain volume 
```{r}
aseg2TPbehav$LHNAccWBVCorrected <- aseg2TPbehav$Left.Accumbens.area/aseg2TPbehav$lhCortexVol

aseg2TPbehav$RHNAccWBVCorrected <- aseg2TPbehav$Right.Accumbens.area/aseg2TPbehav$rhCortexVol
```

Now look at NAcc volume and obesity
```{r}
summary(BMIGroupVolRHAgeCorrected <- lmer(LHNAccWBVCorrected ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))
summary(BMIPercVolRHAgeCorrected <- lmer(RHNAccWBVCorrected ~BMIGroupReduced + AgeCent + (1|ID), data=aseg2TPbehav))
```




